\pkg{depmixS4} : An \proglang{R}-package for hidden Markov models

### 2010-03-04 papers/jss/dpx4Rev.Rnw
Yet more paper updates ...
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/depmix@378 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Two steps are involved in using \pkg{depmixS4} which are illustrated
below with examples:
\begin{enumerate}
	\item model specification with function \code{depmix} (or with \code{mix}
	for latent class and finite mixture models, see example below on adding
	covariates to prior probabilities in section~\ref{sec:prior})

>>>>

Two steps are involved in using \pkg{depmixS4} which are illustrated
below with examples:
\begin{enumerate}
	\item model specification with function \code{depmix} (or with \code{mix}
	for latent class and finite mixture models, see example below on adding
	covariates to prior probabilities)
